---
title: "README"
author: "Krzysztof Kłos"
date: "July 5, 2017"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[![Build Status](https://travis-ci.org/krzyklo/ingaasp2rcpp.svg?branch=master)](https://travis-ci.org/krzyklo/ingaasp2rcpp)

### Intro
This is the R package with model of bandgap(Eg) and strain in InGaAsP material based on paper:  
**J. Minch, S.H. Park, T. Keating, and S.L. Chuang: "Theory and Experiment if InGaAsP and AlInGaAs Long Wavelength Strained Quantum-Well Lasers" from Journal of Quantum Electronic vol 35, NO. 5, May 1999**

The model allows to transform Eg, Strain into molar fractions x(Ga), and y(As) and back:  
$Eg,Strain <--> x,y$
It was also used to exercise good coding practices in R:

- creating R packages
- documenting with Roxygen2 package
- writing unit tests with TestThat package
- using Rcpp for speed of C++
- using Boost C++ library
- writing R markdown documents
- continous integration principle with GitHub and Travis(Linux only)

### Installation
Type the commands below in R or RStudio, you could omit devtools if you already have it. 

`install.packages("devtools")`

`devtools::install_github("krzyklo/ingaasp2rcpp")`

The package location on GitHub: <https://github.com/krzyklo/ingaasp2rcpp>.

### Figures
The figures below shows digitized data (circles) and **InGaAsP calculator** results (lines) for $Eg,Strain <--> x,y$ transformations in both directions.

```{r, echo= FALSE, fig.width=7, fig.height=4, fig.show='hold', fig.cap = "Fig. 1. Calculation of bandgap Eg and Strain from molar fractions X and Y. Reproduced from Fig. 1 b) of the reference paper"}
library("ingaasp2rcpp")
data("fig1b")
par(mar=c(3,3,1.5,0))
plot(fig1b$x,fig1b$y10,t="p",xlim=c(-0.02,0.02),ylim=c(0.4,1.4),main="InGaAsP, calculated overlaid on digitized") #x=0..1, y=1
grid()
lines(ingaasp2rcpp::modPQ_EgStrain(seq(0,1,0.05),1)) #x=0..1, y=1
points(fig1b$x,fig1b$x01,col="blue") #x=0.1, y=0..1
lines(ingaasp2rcpp::modPQ_EgStrain(0.1,seq(0,1,0.05)),col="blue") #x=0.1, y=0..1
points(fig1b$x,fig1b$x0,col="magenta")
lines(ingaasp2rcpp::modPQ_EgStrain(0,seq(0,1,0.05)),col="magenta") #x=0, y=0..1
points(fig1b$x,fig1b$y0,col="brown")
lines(ingaasp2rcpp::modPQ_EgStrain(seq(0,1,0.05),0),col="brown") #x=0..1, y=0
points(fig1b$x,fig1b$y07,col="green")
lines(ingaasp2rcpp::modPQ_EgStrain(seq(0,1,0.05),0.7),col="green") #x=0..1, y=0.7
points(fig1b$x,fig1b$y09,col="orange")
lines(ingaasp2rcpp::modPQ_EgStrain(seq(0,1,0.05),0.9),col="orange") #x=0..1, y=0.9
legend("topleft",col=c("black","blue","magenta","brown","green","orange"),
       lty=1,
       legend=c("x=0..1 y=1","x=0.1  y=0..1","x=0     y=0..1","x=0..1 y=0","x=0..1 y=0.7","x=0..1 y=0.9"),
       lwd=1.5,cex=0.9,bty="n")
 
title(xlab="Strain [absolute units]",ylab="Eg [eV]", line=2, cex.lab=1.1, family="Calibri Light")

```

```{r, echo= FALSE, fig.width=7, fig.height=4, fig.show='hold', fig.cap = "Fig. 2. As molar fraction vs Ga molar fraction for constant strain and bandgap. Reproduced from Fig. 1 a) of the reference paper"}

data("fig1a")
par(mar=c(3,3,1.5,0))
plot(fig1a$x,fig1a$Eg01,t="p",xlim=c(0,1),ylim=c(0,1),main="InGaAsP, calculated overlaid on digitized")
grid()
points(fig1a$x,fig1a$Str0,col="blue") # 0% strain line, y=ax+b - linear relation between them to get 0
lines(modPQ_XY_EgStrain(seq(0.72,1.35,0.05),0),col="red",lwd=2)
lines(modPQ_XY_EgStrain(seq(0.72,1.35,0.05),0.005),col="orange",lwd=1.5) #0.5% strain line
lines(modPQ_XY_EgStrain(seq(0.705,1.2,0.05),-0.005),col="red",lwd=1.5) #-0.5% strain line

points(fig1a$x,fig1a$Str0,col="blue") # 0 strain line, y=ax+b - linear relation between them to get 0 strain
points(fig1a$x,fig1a$Eg4,col="brown") # 
points(fig1a$x,fig1a$Eg02,col="yellow") # 
lines(modPQ_XY_EgStrain(1.3,seq(0,0.055,0.001)),col="black",lwd=1.5) #constant Eg=1.3eV, nonlinear function
lines(modPQ_XY_EgStrain(1,seq(-0.01,0.035,0.001)),col="green",lwd=1.5) #constant Eg=1eV, nonlinear relation in X, Y coordinates
lines(modPQ_XY_EgStrain(1.2,seq(-0.003,0.045,0.001)),col="green",lwd=1.5) #constant Eg=1.2eV,
legend("topleft",col=c("black","yellow","magenta","brown","green","orange"),
       lty=1,
       legend=c("Eg=1.3eV","Eg=","x=0     y=0..1","x=0..1 y=0","x=0..1 y=0.7","x=0..1 y=0.9"),
       lwd=1.5,cex=0.9,bty="n")
```

